---
title: "Week 7, Day 1"
output: html_document
---

```{r setup, include=FALSE}
# We need the PPBDS.data package because it includes the qscores data which we
# will use for this exercise. rsample is a package from the tidymodels
# collection of packages which makes random sample creation easier. See The
# Primer for examples on its use.

knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rsample)
library(tidyverse)
# install.packages("rsample")
```

We learned how to estimate a posterior probability distribution for a single parameter in Chapter 6. But, in doing so, we had to do a lot of work, calculating the joint distribution 
$p(models, data)$ by hand, and then deriving the conditional probability. What a bother! Fortunately, the bootstrap provides an easier and more generalizable approach.

Define the parameter H as the average number of hours of work reported by students for college courses. 



```{r}

nhanes %>%
  bootstraps(times = 100) %>%
  mutate(boot = map(splits, ~analysis(.)))

```



## Scene 1

**Prompt:** Create a tibble called `q_resamples` with three columns: `splits`, `id` and `boot`.  The first two columns are created automatically when you use `rsample::bootstraps()`. The last variable is a list column which includes a tibble with resampled data from `qscores`. There only column you need to keep from `qscores` is `hours`. Refer to Chapter 7 in the *The Primer* for hints.

```{r}

q_resamples <- qscores %>%
  select(hours) %>%
  bootstraps(times = 1000) %>%
  mutate(boot = map(splits, ~analysis(.)))
  


```


## Scene 2

**Prompt:** Add two more columns to `q_resamples`: `hours_sampled` (the vector of hours pulled from each row of `boot`) and `mean_hours` (the mean of each `hours_sampled`). 

```{r}

q_resamples <- qscores %>%
  select(hours) %>%
  bootstraps(times = 1000) %>%
  mutate(boot = map(splits, ~analysis(.))) %>%
  # mutate(hours_sampled = map(boot, ~.$hours)) %>%
  mutate(hours_sampled = map(boot, ~pull(., hours))) %>%
  mutate(mean_hours = map_dbl(hours_sampled, ~mean(., na.rm = TRUE)))


  
```



## Scene 3

**Prompt:** Create a graphic of the posterior probability distribution for H. Interpret it.


```{r}

q_resamples %>%
  ggplot(aes(x = mean_hours, y = after_stat(count/sum(count)))) +
  geom_histogram(bins = 40, fill = "lightblue") +
  # geom_vline(aes(xintercept = mean(mean_hours))) +
  geom_vline(xintercept = mean(qscores$hours)) +
  
  # We need aes() in the first example because mean_hours is not an object by
  # itsefl, but a column in an object. we could've written
  # q_resamples$mean_hours instead, which wouldn't have required aes() because
  # the object q_resamples exists on its own (can be found if we type
  # q_resamples in the console)
  
  theme_linedraw()

```


